Untitled

### 2019-05-28 manuscript/manuscript draft.Rmd
Update manuscript draft.Rmd

#### Database  
Analyses were conducted on data contained in the open-access ForC database [@Anderson-Teixeira2016; @Anderson-Teixeira2018]. This database contains records of field-based measurements of forest carbon stocks and annual fluxes, compiled from previously published studies and existing databases (e.g. ORNL DAAC; Luyssaert etc?).

*Data selection.* ForC contains measures of carbon stocks and fluxes; for the purposes of this analysis only measures of primary productivity were selected from the database. The variables selected were: GPP, NPP, BNPP (total root and fine root), ANPP (total ANPP, foliage, wood and woody stem).  
Sites were excluded from analysis if they were managed, defined as plots that were planted, managed as plantations, irrigated, fertilised or including the term "managed" in their site description. Sites that had experienced significant disturbance were also excluded. Disturbances that justified site exclusion were major cutting or harvesting, and/or burning, flooding, drought and storm events with site mortality >10% of trees.  
There is evidence that stand age influences patterns of primary productivity and carbon allocation in forest ecosystems [@DeLucia2007; @Gillman2015]. To reduce any biasing effects of stand age, stands under 100 years of age were excluded from analysis.

@@

*Climate datasets.* Climate data was extracted from four open-access climate datasets.

*Model specification.*

>>>>

#### Database  
Analyses were conducted on data contained in the open-access ForC database [@Anderson-Teixeira2016; @Anderson-Teixeira2018]. This database contains records of field-based measurements of forest carbon stocks and annual fluxes, compiled from previously published studies and existing databases (e.g. ORNL DAAC; Luyssaert etc?). Additional targeted literature searches were conducted to identify any further available data on primary productivity, with particular focus on old-growth forests in temperate and boreal regions.

**Fig. 1** - Map showing all data used in the anlysis, coded by variable.
![Distribution of carbon data](https://github.com/forc-db/Global_Productivity/blob/master/results/figures/final_figures/maps/distribution_all_variables.png)

*Data selection.* ForC contains measures of carbon stocks and fluxes; for the purposes of this analysis only measures of primary productivity were selected from the database. The variables selected were: GPP, NPP, BNPP (total root and fine root), ANPP (total ANPP, foliage, wood and woody stem).

*[insert table here similar to in trop-forC paper, including information on productivity measures, methods used to estimate, components included etc]*

Sites were excluded from analysis if they were managed, defined as plots that were planted, managed as plantations, irrigated, fertilised or including the term "managed" in their site description. Sites that had experienced significant disturbance were also excluded. Disturbances that justified site exclusion were major cutting or harvesting, and/or burning, flooding, drought and storm events with site mortality >10% of trees.  
There is evidence that stand age influences patterns of primary productivity and carbon allocation in forest ecosystems [@DeLucia2007; @Gillman2015]. To reduce any biasing effects of stand age, stands under 100 years of age were excluded from analysis.

@@

*Climate datasets.* Where site-level data on mean annual temperature, mean annual precipitation, and latitude were available in the primary literature, this data was compiled and entered directly into the ForC database. In addition to this data, climate data for each site was extracted from five open-access climate datasets.

\begin{table}
\centering
\caption{}
\label{table-paramvalues}
\begin{tabular}{ p{4cm} p{4cm} p{4cm} }
\hline \\ [-1.5ex]
Database &amp; Variables downloaded &amp; Citation \\ [1ex]
\hline \\ [-1.5ex]
WorldClim & mean annual temperature; temperature seasonality; annual temperature range; mean annual precipitation & [@Hijmans2005] \\ [1ex]
WorldClim2 & Vapour pressure; solar radiation & [@Fick2017] \\ [1ex]
Climate Research Unit (CRU) time-series dataset v 4.03 & Cloud cover; annual frost days; annual wet days; potential evapotranspiration & [@Harris2014] \\ [1ex]
Global Aridity Index and Potential Evapotranspiration Climate Database & Aridity; potential evapotranspiration & [@Trabucco2018] \\ [1ex]
TerraClimate & Vapour pressure deficit & [@Abatzoglou2018] \\ [1ex]
\hline
\end{tabular}
\end{table}

| Database | Variables downloaded | Citation |
|---------------|-------------------------------------------------|-------------------|
| WorldClim | Mean annual temperature; temperature seasonality; annual temperature range; mean annual precipitation | [@Hijmans2005] |
| WorldClim2 | Vapour pressure; solar radiation | [@Fick2017] |
| Climate Research Unit (CRU) time-series dataset v 4.03 | Cloud cover; annual frost days; annual wet days; potential evapotranspiration | [@Harris2014] |
| Global Aridity Index and Potential Evapotranspiration Climate Database | Aridity; potential evapotranspiration | [@Trabucco2018] |
| TerraClimate | Vapour pressure deficit | [@Abatzoglou2018] |

*Model specification.* The effects of climate and latitude on primary productivity were analysed using mixed effects models using the package 'lme4' in R v. 1.1.463 (cite).
